Left-linear rules in adhesive categories

### 2024-02-12 icalp/fusione.tex
minima su esempio 2.8

\begin{example}
  \label{ex:adhesive}
  Every topos is adhesive~\cite{lack2006toposes}, thus in particular
  $\cat{Set}$ is adhesive. By the closure properties recalled before,
  every presheaf $[\cat{X},\cat{Set}]$ is adhesive and in particular
  the category $\cat{Graph} = [ E \rightrightarrows V, \cat{Set}]$ is
  adhesive where $E \rightrightarrows {V}$ is the two object category
  with two morphisms $s,t \colon{E} \to {V}$. In a similar way,
  various categories of hypergraphs can be shown to be adhesive, while
  the category $\cat{sGraphs}$ of simple graphs, i.e., graphs without
  parallel edges is $\reg{(\cat{sGraphs})}$-adhesive.\todo{Add reference for simple graphs, add
    hierarchical graphs and term
    graphs\cite{castelnovo2023thesis,CastelnovoGM22}).}
\end{example}

>>>>

\begin{example}
  \label{ex:adhesive}
  Every topos is adhesive~\cite{lack2006toposes}, thus in particular
  $\cat{Set}$ is adhesive. By the closure properties recalled before,
  every presheaf $[\cat{X},\cat{Set}]$ is adhesive and in particular
  the category $\cat{Graph} = [ E \rightrightarrows V, \cat{Set}]$ is
  adhesive where $E \rightrightarrows {V}$ is the two object category
  with two morphisms $s,t \colon{E} \to {V}$. In a similar way,
  various categories of hypergraphs can be shown to be adhesive, 
  such as term graphs and hierarchical graphs~\cite{CastelnovoGM24}.
% while the category $\cat{sGraphs}$ of simple graphs, i.e., graphs without
%  parallel edges is $\reg{(\cat{sGraphs})}$-adhesive.\todo{Add reference for simple graphs, add
 %   hierarchical graphs and term
 %   graphs\cite{castelnovo2023thesis,CastelnovoGM22}).}
\end{example}
